### 2018-08-03 mycv/subs/fundings.tex
updates

  \cvhonor
  {Multi-scale crystal plasticity framework for multiphase metals under non-linear forming scenario} %Award
  {NRF-2017R1D1A1B03031052}%EVENT
  {National Science Foundation of Korea} %Location
  {2017-2020} %dates

>>>>

  \cvhonor
  {}
  {}
  {\href{http://www.motie.go.kr/www/main.do}{South Korean Ministry of Trade, Industry and Energy}}
  {2018-2021}

  \cvhonor
  {Multi-scale crystal plasticity framework for multiphase metals under non-linear forming scenario} %Award
  {NRF-2017R1D1A1B03031052}%EVENT
  {NSF of Korea} %Location
  {2017-2020} %dates

### 2018-08-03 mycv/subs/papers.tex
updates

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
  \cventry
  {H. Kim, F Barlat, Y. Lee, S. Zaman, CS Lee, \underline{Y. Jeong}$^*$}
  {A crystal plasticity model for describing the anisotropic hardening behavior of steel sheets during strain-path changes}
  {Submitted}
  {}
%  {International Journal of Plasticity}
%  {Vol. 93 p212-228, 2017} % etcs
  {
  }

>>>>

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
  % ---------------------------------------------------------
  \cventry
  {H. Kim, F Barlat, Y. Lee, S. Zaman, CS Lee, \underline{Y. Jeong}$^*$}
  {\href{https://doi.org/10.1016/j.ijplas.2018.07.010}{A crystal plasticity model for describing the anisotropic hardening behavior of steel sheets during strain-path changes}}
  {International Journal of Plasticity}
  {In press}
  {
  }
